---
title: "Logistic Regression"
author: "Yuheng He"
output: html_notebook
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, error=FALSE)
knitr::opts_chunk$set(out.width="100%", fig.height = 5, split=FALSE, fig.align = "default")
options(dplyr.summarise.inform = FALSE)
```




## Load libraries
```{r, message = FALSE}
library(tidyverse)
library(skimr)      # skimming data frames
library(ggthemes)
library(patchwork)  # combine separate ggplots into the same graphic
library(corrplot)

library(rsample)    # initial_split()
library(DescTools)  # PseudoR2()
library(sjPlot)     # tab_model(), print regression models as HTML table
library(caret)      
library(mlr)        
library(rpart)      
library(rpart.plot)
library(ranger)     
library(lightgbm)   
```

## read data
```{r results=FALSE, warning=FALSE, message=FALSE}
ROOT = "../input/heart-failure-clinical-dataset"
palette_ro = c("#ee2f35", "#fa7211", "#fbd600", "#75c731", "#1fb86e", "#0488cf", "#7b44ab")
df<-  read.csv ("heart_failure_clinical_records_dataset.csv")

```

# Check data {.tabset .tabset-fade .tabset-pills}


## Dataset
```{r}
head(df, 50) %>% 
  DT::datatable()
```



## 数据结构 data structure
```{r}
glimpse(df)
```

## Data summary
```{r}
skim(df)
```

# Data visualizations 数据可视化
change data type to make it easier to handle in future work.


```{r class.source="fold-show"}
f_features = c("anaemia", "diabetes", "high_blood_pressure", "sex", "smoking", "DEATH_EVENT")

df_n <- df
df <- df %>%
  mutate_at(f_features, as.factor)
```



### Features vs target (cuenta)
```{r fig.cap="Fig. 1", fig.height=5}
p1 <- ggplot(df, aes(x = anaemia, fill = DEATH_EVENT)) +
  geom_bar(stat = "count", position = "stack", show.legend = FALSE) +
  scale_x_discrete(labels  = c("0 (False)", "1 (True)"))+
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  labs(x = "Anaemia") +
  theme_minimal(base_size = 12) +
  geom_label(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5),
             size = 5, show.legend = FALSE)

p2 <- ggplot(df, aes(x = diabetes, fill = DEATH_EVENT)) +
  geom_bar(stat = "count", position = "stack", show.legend = FALSE) +
  scale_x_discrete(labels  = c("0 (False)", "1 (True)")) +
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  labs(x = "Diabetes") +
  theme_minimal(base_size = 12) +
  geom_label(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5),
             size = 5, show.legend = FALSE)

p3 <- ggplot(df, aes(x = high_blood_pressure, fill = DEATH_EVENT)) +
  geom_bar(stat = "count", position = "stack", show.legend = FALSE) +
  scale_x_discrete(labels  = c("0 (False)", "1 (True)")) +
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  labs(x = "High blood pressure") +
  theme_minimal(base_size = 12) +
  geom_label(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5),
             size = 5, show.legend = FALSE)

p4 <- ggplot(df, aes(x = sex, fill = DEATH_EVENT)) +
  geom_bar(stat = "count", position = "stack", show.legend = FALSE) +
  scale_x_discrete(labels  = c("0 (Female)", "1 (Male)")) +
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  labs(x = "Sex") +
  theme_minimal(base_size = 12) +
  geom_label(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5),
             size = 5, show.legend = FALSE)

p5 <- ggplot(df, aes(x = smoking, fill = DEATH_EVENT)) +
  geom_bar(stat = "count", position = "stack", show.legend = FALSE) +
  scale_x_discrete(labels  = c("0 (False)", "1 (True)")) +
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  labs(x = "Smoking") +
  theme_minimal(base_size = 12) +
  geom_label(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5),
             size = 5, show.legend = FALSE)

p6 <- ggplot(df, aes(x = DEATH_EVENT, fill = DEATH_EVENT)) +
  geom_bar(stat = "count", position = "stack", show.legend = TRUE) +
  scale_x_discrete(labels  = c("0 (False)", "1 (True)")) +
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  labs(x = "DEATH_EVENT") +
  theme_minimal(base_size = 12) +
  geom_label(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5),
             size = 5, show.legend = FALSE)

((p1 + p2 + p3) / (p4 + p5 + p6)) +
  plot_annotation(title = "Distribution of the binary features and DEATH_EVENT")
```









# Para la diabetes, el sexo y el tabaquismo, hubo poca diferencia en la distribución de la variable objetivo.

# Para anemia y high_blood_pressure, existen algunas diferencias en las distribuciones de las variables objetivas, pero no sabemos si podemos decir que las diferencias son significativas.


The median is indicated by a vertical dashed line.  
 

### Age
```{r fig.cap="Fig. 3", out.width="90%", fig.height=9}
p1 <- ggplot(df, aes(x = age)) + 
  geom_histogram(binwidth = 5, colour = "white", fill = palette_ro[6], alpha = 0.5) +
  geom_density(eval(bquote(aes(y = ..count.. * 5))), colour = palette_ro[6], fill = palette_ro[6], alpha = 0.25) +
    # 5 is binwidth of geom_histogram()
    # binwidth can be calculated from "diff(range(df$age))/20"
  scale_x_continuous(breaks = seq(40, 100, 10)) +
  geom_vline(xintercept = median(df$age), linetype="longdash", colour = palette_ro[6]) +
  annotate(geom = "text",
           x = max(df$age)-5, y = 50,
           label = str_c("Min.     : ", min(df$age),
                         "\nMedian : ", median(df$age),
                         "\nMean    : ", round(mean(df$age), 1),
                         "\nMax.    : ", max(df$age))) +
  labs(title = "age distribution") +
  theme_minimal(base_size = 12)

p2 <- ggplot(df, aes(x = age, fill = DEATH_EVENT)) + 
  # geom_histogram(aes(y=..density..), binwidth = 5, colour = "white", position = "identity", alpha = 0.5) +
  geom_density(alpha = 0.64) +
  scale_fill_manual(values = c(palette_ro[2], palette_ro[7]),
                    name = "DEATH_EVENT",
                    labels = c("0 (False)", "1 (True)")) +
  scale_x_continuous(breaks = seq(40, 100, 10)) +

  geom_vline(xintercept = median(filter(df, DEATH_EVENT == 0)$age), linetype="longdash", colour = palette_ro[2]) +
  geom_vline(xintercept = median(filter(df, DEATH_EVENT == 1)$age), linetype="longdash", colour = palette_ro[7]) +
  annotate(geom = "text",
           x = max(df$age)-10, y = 0.03,
           label = str_c("Survived median: ", median(filter(df, DEATH_EVENT == 0)$age),
                         "\nDead median: ", median(filter(df, DEATH_EVENT == 1)$age))) +

  labs(title = "Relationship between age and DEATH_EVENT") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", legend.direction = "horizontal")

p1 / p2
```


#La edad máxima de los pacientes fue alrededor de los 60 años, y el número de pacientes disminuyó en un patrón en forma de campana alrededor de esa edad.

#Hay una diferencia en la distribución de cada variable objetivo, cuanto más joven es la edad, más difícil es morir; la densidad de probabilidad se invierte después de la edad de poco menos de 70 años.




      

# Data preprocessing
La función `initial_split ()` se usa para dividir el conjunto de trenes y el conjunto de prueba.
Puede dividir el conjunto de datos mientras mantiene la proporción de la variable objetivo especificando "DEATH_EVENT" como argumento "estratos".





```{r class.source="fold-show"}
set.seed(0)
df_split <- initial_split(df, p = 0.8, strata = DEATH_EVENT)
train <- training(df_split)
test <- testing(df_split)
head(train)

set.seed(0)
df_n_split <- initial_split(df_n, p = 0.8, strata = DEATH_EVENT)
train_n <- training(df_n_split)
test_n <- testing(df_n_split)
head(train_n)
```

# Train models and make predictions



## Logistic regression analysis

El análisis de regresión logística es un modelo utilizado para predecir y analizar la probabilidad de ocurrencia de un evento (en este caso, `DEATH_EVENT == 1`).
Al estimar los parámetros (intercepto y coeficientes de regresión) utilizando el método de máxima verosimilitud,
es posible calcular el cambio en las probabilidades (la relación entre la probabilidad de que suceda el evento y la probabilidad de que el evento no suceda)
cuando cambian los valores de las variables explicativas.

#121
```{r}

logistic <- glm(DEATH_EVENT ~ .,
           family=binomial(logit), data=train)
summary(logistic)


```



```{r class.source="fold-show"}
lr1 <- glm(DEATH_EVENT ~ .,
           family=binomial(logit), data=train)
tab_model(lr1, show.r2 = FALSE, transform = NULL,
          digits = 3, digits.p = 4)
PseudoR2(lr1)
```

aqui, `p` represent the significance probability. 
The lower the `p` value of the parameter, the more significant it is, and if the value is higher than 0.05, it is considered not significant. 
We can see that there are many variables in this model that are not statistically significant.


y we will use the stepwise method for variable selection. 
In the stepwise method, the model is recreated many times while changing the selection of explanatory variables. 
The model with a smaller AIC (Akaike Information Criterion; a measure of the balance between the simplicity of the model and the goodness of fit of the model) value is left as the better model.


```{r class.source="fold-show"}
lr2 <- step(lr1)

tab_model(lr2, show.r2 = FALSE, transform = NULL,
          digits = 3, digits.p = 4)
PseudoR2(lr2)
```

#

```{r}
odds <- c(round( exp(lr2$coefficients["age"]*10), digits=3 ),
          round( exp(lr2$coefficients["ejection_fraction"]), digits=3 ),
          round( exp(lr2$coefficients["serum_creatinine"]), digits=3 ),
          round( exp(lr2$coefficients["serum_sodium"]), digits=3 ),
          round( exp(lr2$coefficients["time"]*7), digits=3 ))


data.frame(variables = names(odds), odds = odds) %>%
  mutate(description = c("Odds ratio of death for age 10 years older",
                         "Odds ratio of death if ejection fraction id 1% higher",
                         "Odds ratio of death if serum creatinine level is 1 mg/dL higher",
                         "Odds ratio of death if serum sodium level is 1 mg/dL higher",
                         "Odds ratio of death with 1 week (7 days) longer follow-up time"))
```

#Usaremos este modelo para predecir los datos de prueba.

```{r}
pred <- as.factor(predict(lr2, newdata=test, type="response") >= 0.5) %>%
  fct_recode("0" = "FALSE", "1" = "TRUE")
confusionMatrix(pred, test$DEATH_EVENT, positive = "1")

acc_lr <- confusionMatrix(pred, test$DEATH_EVENT)$overall["Accuracy"]
tpr_lr <- confusionMatrix(pred, test$DEATH_EVENT)$byClass["Specificity"]
# The reason why we set the recall of this model as "Specificity" is because the default value of positive in the confusionMatrix() function is 0.
```

#The prediction using this test data showed that accuracy was 81.36% and recall (`Sensitivity`) was 68.42%.


